Nengo: A Python tool for building large-scale functional brain models

### 2013-10-02 nengo.tex
Edits from Dan's feedback

A node tracks any information
that is not represented by an ensemble.
As a simple example,
a node can be used to model sensory stimuli
that are predefined functions of time.
As a more sophisticated example,
a node can be used to model
a complex experimental environment that
both provides input to the neural model
and responds to the neural model's output.
Nodes allow many of the special-purpose
routines that are necessary in real-world
models to be integrated
as core components of a Nengo model.
This makes Nengo models more explicit,
and enables simulators
to control and optimize node execution.

@@

One of the most common operations done
in Nengo models is circular convolution.
Circular convolution is how
the semantic pointer architecture
(SPA; \cite{TODO})
binds two semantic pointers together.
Binding is central to many
of the high level cognitive tasks
that make Spaun unique.
Circular convolution
is best implemented in a two-layer network,
rather than in a single connection.
This two-layer network construction is simplified
by the existence of the \texttt{CircularConvolution} network.
The complexity encapsulated in that network
can be seen in Figure~\ref{fig:cconv}.

@@

The APIs of Nengo and PyNN are similar,
but differ significantly
in how groups of neurons are connected together.
In Nengo, connections commonly describe
the mathematical operation that is performed
through the connection between
two ensembles;
e.g., \texttt{DecodedConnection(A, B,
function=product)} connects ensemble A
to ensemble B, projecting the product of
some dimensions encoded by A to B.
In PyNN, connections commonly describe
features of the connection weight matrix
between two populations;
e.g., \texttt{FixedProbabilityConnector(0.5)}
connects two ensembles together,
with a probability of 0.5
that there will be a connection
between a pair of neurons in the two populations.
This difference reflects the
fundamental difference that Nengo
is built on a theoretical framework
that enables modellers to think
about information processing in the brain
at a conceptual level.

>>>>

A node represents information
that cannot be decoded from an ensemble.
As a simple example,
a node can be used to model sensory stimuli
that are predefined functions of time.
As a more sophisticated example,
a node can be used to model
a complex experimental environment that
both provides input to the neural model
and responds to the neural model's output.
Nodes allow many of the special-purpose
routines that are necessary in real-world
models to be integrated
as core components of a Nengo model.
This makes Nengo models more explicit,
and enables simulators
to control and optimize node execution.

@@

A common function computed by Nengo models
is circular convolution.
Circular convolution is how
the semantic pointer architecture
(SPA; \cite{TODO})
binds two semantic pointers together.
Binding is central to many
of the high level cognitive tasks
that make Spaun unique.
Circular convolution
is best implemented in a two-layer network,
rather than in a single connection.
This two-layer network construction is simplified
by the existence of the \texttt{CircularConvolution} network.
The complexity encapsulated in that network
can be seen in Figure~\ref{fig:cconv}.

@@

The APIs of Nengo and PyNN are similar,
but differ significantly
in how groups of neurons are connected together.
In Nengo, connections commonly describe
the mathematical operation that is performed
through the connection between
two ensembles;
e.g., \texttt{DecodedConnection(A, B,
function=square)} connects ensemble A
to ensemble B, projecting the square of
the value represented by A to B.
In PyNN, connections commonly describe
features of the connection weight matrix
between two populations;
e.g., \texttt{FixedProbabilityConnector(0.5)}
connects two ensembles together,
with a probability of 0.5
that there will be a connection
between a pair of neurons in the two populations.
This difference reflects the
fundamental difference that Nengo
is built on a theoretical framework
that enables modellers to think
about information processing in the brain
at a conceptual level.
